Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-07-06 doc/main_jfm.tex
updates

%Nature of amphiphilic lipid molecules, small vesicle, GUVs, RBCs, hydrophobic tails interacting with fluid,

%Tank-treading, tumbling, swing vesicles, viscosity ratio

% two-dimensional vesicle, membrane fusion/fissure, self-assembly property,

%crystallization, membrane jiggling can be observed when... the hydrophobicity

%mobility problem, particle suspension, a wide range of study, numerical methods including boundary integral equation method, immersed boundary method, level set method, RCIP kernel splitting method,   vesicle deformations,

% Stokesian dynamics

%The mobility problem can be solved in the fashion of considering propagating waves through rigid bodies where the the external and hydrodynamic forces act as incident fields and scattered field evaluated on the object boundaries.

%The Helfrich membrane energy is well known in continuum modeling/theory. Here we combine the framework in coarse-grained modeling using Janus-type configurations. However,

%Thermal fluctuation effect not considered but the granular system in a fluid

%our approach combines the

\subsection{Hydrophobic Attraction Potential (HAP)}

@@

\section{\label{mobility}Mobility Problem}

@@

For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle-like 
structure consists of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is about 
$8.5$ length units.
The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
to determine the initial configuration for later use such as single and multiple vesicle simulations. This will prevent some numerical instability issues when the minimum of the total energy is not achieved. For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2} shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005t$. In the same figure, the variation of mean particle orientation $\theta$ also decreases as expected. The time step size 
$\Delta t=0.2$ is used for all simulations including the relaxation run.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{relax.eps}
  \caption{Vesicle relaxes under a quiescent flow. The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay.
  }
    \label{figure2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{ArcLength.pdf}
\includegraphics[width=0.45\textwidth]{ReducedArea.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. 
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{N58_parabolic.pdf}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
  }
    \label{figure6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_ext_0.pdf}
\includegraphics[height=1.2in]{N116_ext_2500.pdf}
\includegraphics[height=1.2in]{N116_ext_5000.pdf}
\includegraphics[height=1.2in]{N116_ext_7500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple.
  }
    \label{figure8}
\end{figure}

>>>>

\section{Governing  Equations}
\subsection{Hydrophobic Attraction Potential (HAP)}

@@

\subsection{\label{mobility}Mobility Problem}

@@

For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle-like 
structure consists of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is about 
$8.5$ length units.
The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
to determine the initial configuration for later use such as single and multiple vesicle simulations. This will prevent some numerical instability issues when the minimum of the total energy is not achieved. For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2} shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$. In the same figure, the variation of mean particle orientation $\theta$ also decreases as expected. The time step size 
$\Delta t=0.2$ is used for all simulations including the relaxation run.

\begin{figure}
\centering
\includegraphics[height=2in]{relax.eps}
\includegraphics[height=2in]{relax2.eps}
  \caption{Vesicle relaxes under a quiescent flow. The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively. The red curve shows the decreasing trend of the mean magnitude of particle orientation change. The black dashed line shows the reference of how all magnitudes decay.
  }
    \label{figure2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{-0.5cm}
\includegraphics[height=2in]{ArcLength.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. 
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
  }
    \label{figure6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_ext_0.pdf}
\includegraphics[height=1.2in]{N116_ext_2500.pdf}
\includegraphics[height=1.2in]{N116_ext_5000.pdf}
\includegraphics[height=1.2in]{N116_ext_7500.pdf}
%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple.
  }
    \label{figure8}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_cont_a.pdf}
\includegraphics[height=1.2in]{N116_cont_b.pdf}
\includegraphics[height=1.2in]{N116_cont_c.pdf}
\includegraphics[height=1.2in]{N116_cont_d.pdf}
%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
  }
    \label{figure8}
\end{figure}
